\documentclass[../../main.tex]{subfiles}

\begin{document}
\label{begleitschreiben_interview}

\subsubsection*{Begleitschreiben Interview-Anfrage}
\addcontentsline{toc}{subsubsection}{Begleitschreiben Interview-Anfrage}

\begin{sloppypar}
{\fontfamily{cmtt}\selectfont
\footnotesize

Dear colleagues,

Security Awareness is becoming more and more important for \companyshort. I therefore would like (in consultation with our CISO Nathalie Weiler) to conduct a short, personal interview regarding Security Awareness with you. Such an interview lasts about 30 minutes and takes place only with me. 

The statements made during the interview will be kept confidential, the data collected will be anonymized and stored in encrypted form. It is also only used for the analysis of the interviews. After analysis, the data will be deleted.

Please indicate to me (by either replying to this email or via embedded voting buttons) until middle of next week, if I can invite you to such an interview. You would not have to prepare anything for the interview.

Kind regards,
}
\end{sloppypar}

\vspace{1cm}

\subsubsection*{Begleitschreiben Interview-Termin}
\addcontentsline{toc}{subsubsection}{Begleitschreiben Interview}

\begin{sloppypar}
{\fontfamily{cmtt}\selectfont
\footnotesize

Dear valued colleagues,

Thank you for your willingness and participation in the "`Security Awareness"' interview. The interview is part of a major survey \companyshort is conducting to evaluate the general state of various security aspects. 
Your participation will help us in identifying particular areas of interest and bring the security awareness in the company to a higher level.

I’m looking forward to interviewing you and hearing your opinion about security awareness!

Kind regards,
}

\normalsize

\end{sloppypar}

\end{document}
